The necessity of hypermedia RDF and an approach to achieve it

### 2012-04-12 eswc-2012/workshop2.tex
note hm:mergedInto
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@211 43ef1190-90fd-4dd7-a769-d0121f02b80e
Make RaUL a LT remove RDForms
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@212 43ef1190-90fd-4dd7-a769-d0121f02b80e

We noted that for a read-write RESTful protocol, we need to say in the
RDF message itself what kind of operations can be made. We also note
that only information resources can be manipulated, and we argued that
it should be possible to add the required triples to every
resource. We should be able to define hypermedia RDF in terms of a
minimal vocabulary, but like the H~Factor web page, we will find it
instructive to use examples. In the following, we use Turtle syntax,
with prefixes omitted for brevity. Also, we note that in many cases,
we are making statements about the current resource, which given a
reasonable base URI can be written as \texttt{<>}. We have not found
the following factors to be relevant to RDF: \textsf{LE} (embedded
links), \textsf{CR}, \textsf{CU} (control data for read and update
requests respectively), and \textsf{LT} (templated queries, though the latter may be
supported by RDForms\footnote{\url{http://vocab.deri.ie/rdforms}}?);
and \textsf{LO} and \textsf{CL} are trivially supported. The remaining
are:

@@

@@

>>>>

We noted that for a read-write RESTful protocol, we need to say in the
RDF message itself what kind of operations can be made. We also note
that only information resources can be manipulated, and we argued that
it should be possible to add the required triples to every
resource. We should be able to define hypermedia RDF in terms of a
minimal vocabulary, but like the H~Factor web page, we will find it
instructive to use examples. In the following, we use Turtle syntax,
with prefixes omitted for brevity. Also, we note that in many cases,
we are making statements about the current resource, which given a
reasonable base URI can be written as \texttt{<>}. We have not found
the following factors to be relevant to RDF: \textsf{LE} (embedded
links), \textsf{CR} and \textsf{CU} (control data for read and update
requests respectively); and \textsf{LO} and \textsf{CL} are trivially
supported. The remaining are:

@@

\item[\textsf{LT}] Support for templated queries (HTTP GET)

The RaUL\footnote{\url{http://vocab.deri.ie/raul}} goes beyond HTTP
GET queries, but can be used to formulate templated queries similar to
those in HTML, or indeed to generate HTML fragments for the same purpose.

@@

Also note the \texttt{hm:mergedInto} term was motivated by that POST
operations in this specification results in an RDF Merge of the
payload into the named graph.
